---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# personalized.help

<!-- badges: start -->
<!-- badges: end -->

The goal of personalized.help is to demonstrate how you can create some content of a manual page in an R package _on the fly_, inspired by a conversation in the rOpenSci slack workspace.

## Installation

You can install the development version of personalized.help like so:

``` r
pak::pak("maelle/personalized.help")
```

## Example

Imagine I, Maëlle Salmon, load the help page for thing.
Notice how the help page says "hello" to _me_.

```{r eval=FALSE, echo=TRUE}
library(personalized.help)
?thing
```

```{r eval=TRUE, echo=FALSE, results='asis'}
library(personalized.help)
# https://stackoverflow.com/questions/63677870/how-do-you-make-output-from-help-function-display-in-rmarkdown-document
helpfile <- utils:::.getHelpFile(help(thing))
outfile <- withr::local_tempfile(fileext = ".html")
tools:::Rd2HTML(helpfile, out = outfile)
html <- brio::read_lines(outfile)
html <- html[grep("\\<h2\\>", html):length(html)]
html <- paste(html, collapse = "\n")
cat(c("```html\n", html, "\n```\n"))
```

Now what if you, Awesome Person, do that?
To trick whoami to think I am you I am setting the `FULLNAME` environment variable to your name.

The help page says hello to you using your name!

```{r eval=FALSE, echo=TRUE}
library(personalized.help)
withr::local_envvar(FULLNAME = "Awesome Person")
?thing
```

```{r eval=TRUE, echo=FALSE, results='asis'}
library(personalized.help)
# https://stackoverflow.com/questions/63677870/how-do-you-make-output-from-help-function-display-in-rmarkdown-document
withr::local_envvar(FULLNAME = "Awesome Person")
helpfile <- utils:::.getHelpFile(help(thing))
outfile <- withr::local_tempfile(fileext = ".html")
tools:::Rd2HTML(helpfile, out = outfile)
html <- brio::read_lines(outfile)
html <- html[grep("\\<h2\\>", html):length(html)]
html <- paste(html, collapse = "\n")
cat(c("```html\n", html, "\n```\n"))
```

## How it works

The source of the help of `thing()` has, in lieu of an actual description, this:

```r
#' \Sexpr[results=rd,stage=render]{personalized.help:::generate_help()}
```

where `generate_help()` is this internal function:

```r
generate_help <- function() {
  sprintf("Hello %s!", whoami::fullname(fallback = "human"))
}
```

`generate_help()` gets executed every time the help page is loaded.
It gets the name of the user using the whoami package.

[Real example on CRAN](https://github.com/cran/stevedore/blob/74b63bfcff2af200367fbd78febfd2d36855d500/R/help.R#L4).
[More examples](https://github.com/search?q=\Sexpr[results%3Drd%2Cstage%3Drender]+user%3Acran&type=code&ref=advsearch).
